Evaluating Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe using radiocarbon data

### 2019-03-28 article/02_Materials_and_Methods.Rmd
some more love for Table 1

The resulting dataset is structured as a table with `r r("gpr size", sf_desc)` rows each representing one grave as compiled by `r r("dpr size", sf_desc)` ^14^C dates from `r r("dpr sites amount", sf_desc)` sites. The graves are linked to `r r("dpr period amount", sf_desc)` different *period* terms and `r r("dpr culture amount", sf_desc)` different archaeological *cultures* as they are distinguished in Radon-B. `r r("dpr material bone amount", sf_desc)` dates were measured on sample material of bones and teeth (at least `r r("dpr material cremated bones amount", sf_desc)` of them burnt), `r r("dpr material charcoal wood amount", sf_desc)` on wood and charcoal, a small part (`r r("dpr material other amount", sf_desc)`) on other materials such as nuts, resin or pitch. For the remaining `r r("dpr material unknown amount", sf_desc)` dates, no material information is stored. Regarding the variables burial type and burial construction, the conditions shown in Table \ref{tab:dprcrosstab} apply.

```{r dprcrosstab, echo=FALSE, tidy=FALSE}
load("../analysis/data/output_data/dprcrosstab.RData")
colnames(dprcrosstab)[1:2] <- c("Region", "Burial type")
dprcrosstab %>% 
  dplyr::mutate_at(
    dplyr::vars(tidyselect::one_of("flat", "mound", "unknown")),
    list(~kableExtra::cell_spec(., "latex", bold = . > 100)) 
  ) %>%
  knitr::kable(
    caption = "Burial rite distribution in the active dataset.",
    format = "latex",
    booktabs = T,
    escape = F,
    #linesep = "\\addlinespace \\hline \\addlinespace",
    align = "l"
  ) %>%
  kableExtra::kable_styling(
    full_width = T,
    font_size = 9,
    latex_options = "hold_position"
  ) %>%
  kableExtra::add_header_above(c(" " = 1, " " = 1, "Burial construction" = 3)) %>%
  kableExtra::column_spec(1, width = "2.5cm") %>%
  kableExtra::column_spec(2, width = "1.5 cm") %>%
  kableExtra::column_spec(3:5, width = "0.8cm") %>%
  kableExtra::collapse_rows(1, row_group_label_position = "identity", valign = "top")

>>>>

The resulting dataset is structured as a table with `r r("gpr size", sf_desc)` rows each representing one grave as compiled by `r r("dpr size", sf_desc)` ^14^C dates from `r r("dpr sites amount", sf_desc)` sites. The graves are linked to `r r("dpr period amount", sf_desc)` different *period* terms and `r r("dpr culture amount", sf_desc)` different archaeological *cultures* as they are distinguished in Radon-B.

`r r("dpr material bone amount", sf_desc)` dates were measured on sample material of bones and teeth (at least `r r("dpr material cremated bones amount", sf_desc)` of them burnt), `r r("dpr material charcoal wood amount", sf_desc)` on wood and charcoal, a small part (`r r("dpr material other amount", sf_desc)`) on other materials such as nuts, resin or pitch. For the remaining `r r("dpr material unknown amount", sf_desc)` dates, no material information is stored.

Regarding the variables burial type and burial construction in the grave dataset, the conditions shown in Table \ref{tab:gprcrosstab} apply.

```{r gprcrosstab, echo=FALSE, tidy=FALSE}
load("../analysis/data/output_data/gprcrosstab.RData")
colnames(gprcrosstab)[1:2] <- c("Region", "Burial type")
gprcrosstab %>% 
  dplyr::mutate_at(
    dplyr::vars(tidyselect::one_of("flat", "mound", "unknown")),
    list(
      ~kableExtra::cell_spec(., "latex", bold = . > 100, color = ifelse(. < 10, "red", "black"))
    ) 
  ) %>%
  knitr::kable(
    caption = "Burial rite distribution in the active dataset.",
    format = "latex",
    booktabs = T,
    escape = F,
    align = "l"
  ) %>%
  kableExtra::kable_styling(
    full_width = T,
    font_size = 9,
    latex_options = "hold_position"
  ) %>%
  kableExtra::add_header_above(c(" " = 1, " " = 1, "Burial construction" = 3)) %>%
  kableExtra::column_spec(1, width = "2 cm") %>%
  kableExtra::column_spec(2, width = "1.5 cm") %>%
  kableExtra::column_spec(3:5, width = "0.8cm") %>%
  kableExtra::collapse_rows(1, row_group_label_position = "identity", valign = "top")
